Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-07-31 tex/comments/3-nat-comments.tex
One more Heuristics revision

>>>>

A potential extension of this work is to implement a standard basis for the Specht module (e.g. the Murphy basis \cite{Murphy1,Murphy2}) in order to draw explicit isomorphisms between the Specht module and crossingless matchings representation, rather than the implicit isomorphisms proven in \ref{Correspondence Theorem}.
